Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Alternative section titles
BCP: Adapt Arbitrary instance

\begin{quote}
    TBD: This section needs more work, to get the wording right.
\end{quote}

Haddock version 2.7.2 and earlier provided markup syntax for
code blocks, but did not provide any markup syntax for evidence.
As we described, we implemented markup support for interactive examples ({\tt >>>}) in 2010.
It is available in Haddock version 2.8 or later.
We also extended Haddock to support markup for properties ({\tt prop>}) which
will be available with a future release of Haddock.
Both interactive examples and properties in Haddock comments are
include into generated documentation.

@@

\subsubsection{Step 2}

@@

\subsubsection{Step 3}

@@

>>>>

Haddock before version 2.8 had markup syntax for
code blocks, but no markup syntax for evidence.
As mentioned before, we implemented support for interactive examples ({\tt >>>}) in 2010.
It is available in Haddock version 2.8 or later.
We also added support for markup of properties ({\tt prop>}) which
will be available in a future release of Haddock.
Both interactive examples and properties in Haddock comments are
included in the generated documentation.

@@

\subsubsection{Get it right}

@@

\subsubsection{Get it fast}

@@

\noindent TBD: With a much more efficient implementation at hand, we
can also adapt our definition of ``small non-negative number'', so
that a wide range of input values is tested:

\begin{quote}
\small
\begin{verbatim}
instance Arbitrary Small where
  arbitrary = Small . (`mod` 1000) <$> arbitrary
\end{verbatim}
\end{quote}
